\chapter{Course Policy FAQ}

\section{Can I email you an essay or draft when it is due?}
\begin{itemize}

\item {\Large \color{Ahrenge}\textbf{No.}} 
\end{itemize}

However, in order to prevent your essay from being late you may email a copy as a placeholder until you turn in a paper copy. This might happen if your printer fails or you spill coffee on your essay. Please ensure that the paper copy you hand in later is identical in very way to your electronic placeholder.


\section{Can I email you an essay for extra comments?}
\begin{itemize}

\item {\Large \color{Ahrenge}\textbf{No.}} 
\end{itemize}


I usually do not take requests for extra comments via email unless there is no other possible way a student can meet with me in person. \textbf{However, I am happy to discuss new drafts with students during office hours or at other times by appointment}. Considering how easy it is to attach a file to an email, almost every student would seek this additional help. As a result, I would be deluged with requests for help, often at the very last minute. These requests would become so numerous that it would be impossible for me to thoughtfully respond to them all. And it wouldn’t be fair to help some students and not others. \emph{More significantly, I think this practice also sends the wrong message that I am your personal editor}. That really isn’t my job.

\section{Can I bring my laptop to our office meeting?}
\begin{itemize}
\item {\Large \color{Ahrenge}\textbf{No.}} 

I try to save the trees as much as possible. However, I have discovered that under these circumstances students often type the words that I say directly into their papers. This potentially blurs the line between critique and authorship. Since it is important that you do your own work, it is best to avoid this problem/temptation by using a hard copy.
\end{itemize}

\section{I can't make office hours; can we meet another time?}
\begin{itemize}
\item {\Large \color{Ahrenge}\textbf{Yes.}} 

I will be happy to accommodate students whose schedules conflict with my office hours. Contact me and we can work out the details. If we are unable to find a time that works for both of us, the \href{https://students.dartmouth.edu/rwit/}{RWIT} is another excellent option.
\end{itemize}

\section{Can I have an extension?}
\begin{itemize}
\item {\Large \color{Ahrenge}\textbf{Sort of.}} 

I must be fair to all of my students. If I give an extension to one student, the other students who turned in their essays on time are disadvantaged. For that reason I deduct a full letter grade for each day an assignment is late. Take as much extra time as you wish; however, you should be prepared to face the consequences. Of course, if you have a serious emergency that prevents you from completing work, I will be happy to work out a new due date.
\end{itemize}

\section{Do you have a grading rubric?}
\begin{itemize}
\item {\Large \color{Ahrenge}\textbf{Yes and No.}} 

I do not have a formalized rubric to explain the exact nature of the A, B, C, D, and F essay. However, \hyperlink{good-writing}{\color{Ahrenge}{here is an explanation of what I value in good academic writing}}. 

\end{itemize}
